\begin{longtable}{llcc}
\caption{Dataset Description by Country} \label{tab:dataset_all} \\
\toprule
Variable & Code & Unit Root & Transform. \\
\midrule
\endfirsthead
\toprule
Variable & Code & Unit Root & Transform. \\
\midrule
\endhead
\bottomrule
\endfoot
\textit{China} & & & \\
CPI (All Items, Growth) & \texttt{CPALTT01CNM657N} & No & $(X_m - \mu_j)/\sigma_j$ \\
PPI (Furniture, Household) & \texttt{WPU1261} & Yes & $\Delta\log(X_m)$ \\
Total Reserves (excl.\ gold) & \texttt{TRESEGCNM052N} & Yes & $\Delta\log(X_m)$ \\
Exports & \texttt{XTEXVA01CNM664S} & Yes & $\Delta\log(X_m)$ \\
Imports & \texttt{XTIMVA01CNM664S} & Yes & $\Delta\log(X_m)$ \\
Exchange Rate (RMB/USD) & \texttt{EXCHUS} & Yes & $\Delta\log(X_m)$ \\
Policy Uncertainty & \texttt{CHNMAINLANDEPU} & Yes & $\Delta\log(X_m)$ \\
US Imports from China & \texttt{IMPCH} & Yes & $\Delta\log(X_m)$ \\
Effective Exchange Rate & \texttt{RBCNBIS} & Yes & $\Delta\log(X_m)$ \\
SSEC Index & \texttt{Investing.com} & Yes & $\Delta\log(X_m)$ \\
Real GDP & \texttt{CHNGDPNQDSMEI} & --- & $\Delta\log(\text{GDP}_q)$ \\
\addlinespace
\textit{Germany} & & & \\
CPI (All Items) & \texttt{DEUCPIALLMINMEI} & Yes & $\Delta\log(X_m)$ \\
Unemployment Rate & \texttt{LRHUTTTTDEM156S} & Yes & $\Delta\log(X_m)$ \\
Production Volume & \texttt{DEUPROINDMISMEI} & Yes & $\Delta\log(X_m)$ \\
Retail Trade & \texttt{DEUSARTMISMEI} & Yes & $\Delta\log(X_m)$ \\
Exports & \texttt{XTEXVA01DEM664S} & Yes & $\Delta\log(X_m)$ \\
Imports & \texttt{XTIMVA01DEM664S} & Yes & $\Delta\log(X_m)$ \\
Total Reserves (excl.\ gold) & \texttt{TRESEGDEM052N} & Yes & $\Delta\log(X_m)$ \\
Exchange Rate & \texttt{CCUSMA02DEM650N} & No & $(X_m - \mu_j)/\sigma_j$ \\
Effective Exchange Rate & \texttt{RNDEBIS} & Yes & $\Delta\log(X_m)$ \\
Policy Uncertainty & \texttt{EUEPUINDXM} & Yes & $\Delta\log(X_m)$ \\
DAX Index & \texttt{Yahoo Finance} & Yes & $\Delta\log(X_m)$ \\
Real GDP & \texttt{CLVMNACSCAB1GQDE} & --- & $\Delta\log(\text{GDP}_q)$ \\
Price Competitiveness & \texttt{Bundesbank} & Yes & $\Delta\log(X_m)$ \\
\addlinespace
\textit{UK} & & & \\
Share Prices & \texttt{SPASTT01GBM661N} & Yes & $\Delta\log(X_m)$ \\
CPI (All Items) & \texttt{GBRCPIALLMINMEI} & Yes & $\Delta\log(X_m)$ \\
Production Volume & \texttt{GBRPROINDMISMEI} & Yes & $\Delta\log(X_m)$ \\
Interest Rate (Gov Bond) & \texttt{INTGSBGBM193N} & Yes & $\Delta X_m$ \\
Interest Rate (10Y Gov) & \texttt{IRLTLT01GBM156N} & Yes & $\Delta X_m$ \\
Total Reserves (excl.\ gold) & \texttt{TRESEGGBM052N} & Yes & $\Delta\log(X_m)$ \\
Exchange Rate (GBP/USD) & \texttt{EXUSUK} & Yes & $\Delta\log(X_m)$ \\
Imports & \texttt{XTIMVA01GBM664S} & Yes & $\Delta\log(X_m)$ \\
Exports & \texttt{XTEXVA01GBM664S} & Yes & $\Delta\log(X_m)$ \\
Unemployment Rate & \texttt{ONS} & Yes & $\Delta\log(X_m)$ \\
FTSE 100 Index & \texttt{Yahoo Finance} & Yes & $\Delta\log(X_m)$ \\
Real GDP & \texttt{NGDPRSAXDCGBQ} & --- & $\Delta\log(\text{GDP}_q)$ \\
M1 Money Stock & \texttt{BOE} & Yes & $\Delta\log(X_m)$ \\
Employment Rate & \texttt{ONS} & Yes & $\Delta\log(X_m)$ \\
\addlinespace
\textit{US} & & & \\
Avg.\ Weekly Hours, Manuf. & \texttt{AWHMAN} & No & $(X_m - \mu_j)/\sigma_j$ \\
CPI (All Items) & \texttt{CPIAUCSL} & Yes & $\Delta\log(X_m)$ \\
Industrial Production & \texttt{INDPRO} & Yes & $\Delta\log(X_m)$ \\
Real Personal Consum. & \texttt{DPCERA3M086SBEA} & Yes & $\Delta\log(X_m)$ \\
Effective Fed Funds Rate & \texttt{FEDFUNDS} & No & $(X_m - \mu_j)/\sigma_j$ \\
Interest Rate (10Y Trea.) & \texttt{GS10} & Yes & $\Delta X_m$ \\
S\&P 500 Volatility & \texttt{VIXCLS} & No & $(X_m - \mu_j)/\sigma_j$ \\
Unemployment Rate & \texttt{UNRATE} & No & $(X_m - \mu_j)/\sigma_j$ \\
Nonfarm Payroll Emp. & \texttt{PAYEMS} & Yes & $\Delta\log(X_m)$ \\
Labor Force Participation & \texttt{CIVPART} & Yes & $\Delta\log(X_m)$ \\
M1 Money Stock & \texttt{M1SL} & Yes & $\Delta\log(X_m)$ \\
M2 Money Stock & \texttt{M2SL} & Yes & $\Delta\log(X_m)$ \\
Net Exports & \texttt{BOPTEXP} & Yes & $\Delta\log(X_m)$ \\
Moody's AAA Bond Yield & \texttt{AAA} & Yes & $\Delta X_m$ \\
S\&P 500 Index & \texttt{Yahoo Finance} & Yes & $\Delta\log(X_m)$ \\
Real GDP & \texttt{GDPC1} & --- & $\Delta\log(\text{GDP}_q)$ \\
\addlinespace
\end{longtable}
\vspace{0.5em}
\noindent{\footnotesize \textit{Note}: Most series are from FRED. Stock indices are from Yahoo Finance. SSEC Index is from Investing.com. UK M1 and employment data are from BOE/ONS. Germany price competitiveness is from the Deutsche Bundesbank. ``Unit Root'' indicates non-stationarity based on the Augmented Dickey-Fuller test at the 5\% level and economic considerations. $\Delta\log(X_m)$: log-difference; $\Delta X_m$: first-difference (applied to interest rates); $(X_m - \mu_j)/\sigma_j$: Z-score standardization.}